Supplementary Information

### 2015-06-22 manuscript/supplement.tex
Got the correct reference for Brose

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used to assess the roles
  of parasites within food webs. As all but 3 of the webs from~\citet{GlobalWeb} contained only
  free-living species, we removed the the parasites (and all interactions involving them) from
  these webs (and the 3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living 
  species only. In addition, we included the 96 webs from~\citet{Brose2006}, which were originally
  collected to XXXYYYY. This gave us a database of 259 webs. As we wished to use the
  logarithmic form of power-law relationships, we then eliminated any food web which did not have
  at least one each of basal resources, intermediate consumers, and top predators (to obtain non-zero
  proportions of each category). Our final sample size was thereby reduced to 163 food webs.

>>>>

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used to assess the roles
  of parasites within food webs. As all but 3 of the webs from~\citet{GlobalWeb} contained only
  free-living species, we removed the the parasites (and all interactions involving them) from
  these webs (and the 3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living 
  species only. In addition, we included 12 of the 96 webs from~\citet{Brose2005}, which were originally
  collected to test the relationship between consumer and
  resources body sizes. The remaining webs the~\citet{Brose2005}
  dataset were also included in the~\citet{GlobalWeb} 
  dataset. This gave us a database of 259 webs. As we
  wished to use the logarithmic form of power-law
  relationships, we then eliminated any food web which
  did not have at least one each of basal resources,
  intermediate consumers, and top predators (to obtain 
  non-zero proportions of each category). Our final sample
  size was thereby reduced to 163 food webs.
